Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-04 vesicle_code/docs/permeableVes/main.tex
rearranged figures a bit
yny

% Please add a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement
about the significance of their research paper written at a level
understandable to an undergraduate educated scientist outside their
field of speciality. The primary goal of the significance statement is
to explain the relevance of the work in broad context to a broad
readership. The significance statement appears in the paper itself and
is required for all research papers.}

@@

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Provided that the bilayer structure stays intact (no membrane poration or rupture) under load, the water influx/efflux is
often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations. 
  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero
  thickness and an outward normal $\nn$) is permeable to water
  molecules, depending on the mechanical normal stress balance on the
  membrane.  The slipper in (a) is the steady-state shape of a
  semipermeable vesicle in a Poiseuille flow.}
\end{figure}

@@

%\begin{figure*}[htp]
%  \ifTikz
%  \input{figures/stenosisComposite.tikz}
%  \else
%  \includegraphics{figures/stenosisComposite.pdf}
%  \fi
%  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
%  passing through a constricted geometry similar to the experimental
%  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
%  through a constricted geometry that is over five times longer. (c):
%  The excess pressure of an impermeable and semipermeable vesicle in the
%  short geometry in (a). (d): The reduced area of the semipermeable
%  vesicles in the geometries in (a) and (b) as a function of the
%  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
%  half the length of the constriction. (e) The reduced area of the
%  semipermeable vesicles in the geometries in (a) and (b) as a function
%  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
%  residency time. In parts (c) and (d), the dashed lines correspond to
%  the locations of the inlet and outlet. In part (e), the dashed lines
%  correspond to the times that the vesicle enters and exits the
%  constriction. The colored vesicles show the tension distribution in
%  N/m of the circled vesicles. Throughout the entire simulation, these
%  vesicle configurations have the largest tension.}
%\end{figure*}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.\todo[inline]{Make the
  time steps equispaced and the values of $x$ non-uniform. Reverse their
  orders between to and bottom.}}
\end{figure}

@@

To understand the effects of water permeability on cells that repeatedly
go through micro-capillary vessels or sub-micron slits, we construct a
contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
simulate a vesicle passing through the contracting geometry six times.
In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
deflates each time it passes through the contraction followed by a
gradual inflation (over seconds). The total area loss over the history
of the vesicle is almost 50\%. In
Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
a function of the vesicle's center of mass. As the vesicle passes
through the contraction, it first accelerates until it reaches the neck
where it abruptly decelerates to go through the contraction. The
variation of the reduced area and velocity with respect to time are also
shown in Figure~\ref{fig:contractingComposite2}.

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{This work focuses on effects of membrane permeability to water on the hydrodynamics of a vesicle (self-enclosing lipid bilayer membrane) under flows and/or confinement. Without membrane poration or rupture, we use direct numerical simulations to illustrate that over sufficiently long time the water permeability does affect the equilibrium vesicle shapes in open space. Under confinement, we show that water permeability may be quickly amplified to induce significant change in shape as the vesicle goes through a closely-fit long channel and a narrow slit. These results provide a quantitative measure of membrane permeability to water in terms of vesicle inflation/deflation under load.
%
%Authors must submit a 120-word maximum statement
%about the significance of their research paper written at a level
%understandable to an undergraduate educated scientist outside their
%field of speciality. The primary goal of the significance statement is
%to explain the relevance of the work in broad context to a broad
%readership. The significance statement appears in the paper itself and
%is required for all research papers.
%
}

@@

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations. 
  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero
  thickness and an outward normal $\nn$) is permeable to water
  molecules, depending on the mechanical normal stress balance on the
  membrane.  The slipper in (a) is the steady-state shape of a
  semipermeable vesicle in a Poiseuille flow. \todo[inline]{Fix font
  size of block (d)}}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry}

@@

To understand the effects of water permeability on cells that repeatedly
go through micro-capillary vessels or sub-micron slits, we construct a
contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
simulate a vesicle passing through the contracting geometry six times.
In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
deflates each time it passes through the contraction followed by a
gradual inflation (over seconds). The total area loss over the history
of the vesicle is almost 50\%. In
Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
a function of the vesicle's center of mass. As the vesicle passes
through the contraction, it first accelerates until it reaches the neck
where it abruptly decelerates to go through the contraction. The
variation of the reduced area and velocity with respect to time are also
shown in Figure~\ref{fig:contractingComposite2}.
\begin{figure}[hbp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.\todo[inline]{Make the
  time steps equispaced and the values of $x$ non-uniform. Reverse their
  orders between to and bottom.}}
\end{figure}
